### 2013-10-18 manuscripts/reply/reply-main.tex
Incorporating comments from Mark.

Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses
showing that \msb can often be biased toward inferring models of temporally
clustered divergence times across taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the poor behavior of the method
is likely the low marginal likelihoods of parameter-rich models integrated over
vast parameter space with low probability of producing the data, yet relatively
high prior density \citep{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be increasingly biased as
the overall space of the model increases, either as a function of the number of
taxon pairs or the width of the uniform priors on nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument
that focuses on only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian reasoning and
questionable assumptions, and does not explain the bias of the method found in
many of the analyses of \citet{Oaks2012}. 
Furthermore, we present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the poor behavior of \msb.

@@

To mitigate the bias, \citet{Oaks2012} suggest alternative prior probability
distributions on divergence models and nuisance parameters could increase the
likelihoods of models with more divergence time parameters.
They also describe simulation-based procedures for determining power, accuracy,
and robustness of the method given a dataset, and recommend any application of
\msb should be accompanied by such procedures.
Alternatively, \citet{Hickerson2013} present an approximate Bayesian
model-averaging approach for accommodating uncertainty in selecting among
empirically guided priors, and champion the method as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
We discuss errors in this approach that render some of their results invalid
and leave the remaining results difficult to interpret.
Furthermore, we follow the recommendations of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the model-averaging approach of
\citet{Hickerson2013} is biased toward clustered divergence models and
predisposed to excluding true parameter space.
The model-averaging approach provides another means by which the model can
``escape'' large parameter space, and the method's bias toward smaller models
remains.
This manifestation of the bias often excludes the true parameter space due to
the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.
% which is used and encouraged by
% \citet{Hickerson2013} without discussing its potential complications.

@@

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to many powerful inference methods.
However, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

The results of our empirical and simulation-based analyses clearly demonstrate
the danger of using narrow, empirically guided uniform priors in a Bayesian
model-averaging framework.
This is especially concerning in \msb, which has already been demonstrated to
be biased away from models with more parameter space \citep{Oaks2012}.
The consequence of this approach is a high risk of obtaining a model-averaged
posterior estimate that is heavily weighted toward incorrect models that
exclude true values of model parameters.

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigator's choice of priors after having seen the resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
    Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before
performing the analysis.

@@

Also, \citet{Hickerson2013} present information only on the extreme case of a
single divergence event.
As discussed in \citet{Oaks2012}, it seems odd to consider the estimation
of two divergence events as a success when divergence is random over hundreds
of thousands (or millions) of generations.
In an empirical system such as the Philippines, where island fragmentation has
occurred at least 10 times over the past several millions of years
\citep{Haq1987,Rohling1998,Siddall2003,Miller2005}, an estimate where 22 taxa
share even a handful of divergence events would be of biogeographic interest.

Lastly, \citet{Hickerson2013} translate their results from units of
\globalcoalunit generations to generations assuming a mutation rate of
$1.92\e{-8}$ mutations per site per generation.
If we translate their results to a scale more consistent with rates of mutation
of nuclear loci ($1\e{-9}$), even under the very optimistic prior settings used
by \citet{Hickerson2013} the method can only reliably reject the extreme case
of one divergence event when divergences are random over a period of more than
3 million generations.
Again, considering \citet{Hickerson2013} are assuming prior knowledge that
all population pairs diverged within the last coalescent unit, this
does not seem particularly powerful.

@@

Our results presented above that demonstrate the bias of the model-averaging
approach of \citet{Hickerson2013} both toward models with narrower \divt{}
priors (Table~\ref{tabModelChoiceEmpirical} and
Figs.~\labelcref{figExclusionSimTau,figExclusionSimProb,figPowerNumExcluded,figPowerProbExclusion})
and models with fewer \divt{} parameters (Figs.~\ref{figPowerPsiMode} \&
\ref{figPowerOmegaProb}) strongly suggest the primary cause is the uniform
priors reducing the marginal likelihoods of large models.
In all of our model-averaging analyses, all prior models have the same number
of samples.
Thus, it is difficult to explain the method's propensity toward the model with
the smallest parameter space via insufficient prior sampling.
While analyses that sample each model proportional to their relative parameter
space could be explored, it seems much more likely that the broad uniform
priors are simply inhibiting the marginal likelihoods of spacious models.

@@

In theory, the approach of \citet{Hickerson2013} is very appealing.  It sums
over multiple candidate prior models to produce a posterior estimate
marginalized over the uncertainty in prior choice.
In general, Bayesian model-averaging is a powerful approach that leverages a
great strength of Bayesian statistical procedures, namely the ability to
obtain marginalized estimates that incorporate uncertainty in nuisance
parameters.
However, given the basic \msb model is already struggling to estimate
a huge number of parameters and model probabilities with scant information
from the data, it is not surprising that adding an additional layer of
model choice to the method causes problems.

@@

Importantly, there is no cost to this strategy.
Given that ABC methods only need to draw random values from prior distributions
(hence there are no difficult prior and proposal ratios to calculate, etc.) it
is easy to use the most appropriate distributions on parameters.
Also, this approach reduces the temptation of empirically guided priors.
The investigator can place the majority of the prior density in regions of
parameter space they believe, \emph{a priori}, are most plausible, but still
capture uncertainty in the tails of distributions with low density.
As discussed in \citet{Oaks2012} the use of uniform priors necessitate
broad priors to avoid excluding the truth \emph{a priori}.
Thus, to avoid the behavior of the method under these uniform priors, using the
data is a very tempting, albeit risky, option \citep{Hickerson2013}.
More appropriate prior distributions would alleviate this issue.

>>>>

Recently, the journal \emph{Evolution} has served as a medium for a discussion
of the potential pitfalls of approximate Bayesian methods of comparative
phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses
showing that \msb can often be biased toward inferring models of temporally
clustered divergence times across taxon pairs.
\citet{Hickerson2013} published a response to \citet{Oaks2012} where they
present an empirical Bayes model-averaging approach that they conclude
circumvents the poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the poor behavior of the method
is likely the low marginal likelihoods of parameter-rich models integrated over
vast parameter space with low probability of producing the data, yet relatively
high prior density \citep{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be increasingly biased as
the overall space of the model increases, either as a function of the number of
taxon pairs or the width of the uniform priors on nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument
that focuses on only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian reasoning and
questionable assumptions, and does not explain the bias of the method found in
many of the analyses of \citet{Oaks2012}. 
Furthermore, we present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

@@

To mitigate the bias, \citet{Oaks2012} suggest alternative prior probability
distributions on divergence models and nuisance parameters could increase the
likelihoods of models with more divergence time parameters.
They also describe simulation-based procedures for determining power, accuracy,
and robustness of the method given a dataset, and recommend any application of
\msb should be accompanied by such procedures.
Alternatively, \citet{Hickerson2013} present an approximate Bayesian
model-averaging approach for accommodating uncertainty in selecting among
empirically guided priors, and champion the method as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
We discuss errors in this approach that render some of their results invalid
and leave the remaining results difficult to interpret.
Furthermore, we follow the recommendations of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the empirical Bayesian approach of
\citet{Hickerson2013} is biased toward clustered divergence models and
predisposed to excluding true parameter space.
The model-averaging approach provides another means by which the model can
``escape'' large parameter space, and the method's bias toward smaller models
remains.
This manifestation of the bias often excludes the true parameter space due to
the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice.
% which is used and encouraged by
% \citet{Hickerson2013} without discussing its potential complications.

@@

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model as new information becomes available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

This is not to say that empirical Bayesian approaches are not useful.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to many powerful inference methods.
However, empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citep[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and incorrectly shaped;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods can provide a powerful means of parameter
estimation that often exhibit favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often exhibit well-behaved frequentist coverage
probabilities
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

@@

The results of our empirical and simulation-based analyses clearly demonstrate
the danger of using narrow, empirically guided uniform priors in a Bayesian
model-averaging framework.
% This is especially concerning in \msb, which has already been demonstrated to
% be biased away from models with more parameter space \citep{Oaks2012}.
The consequence of this approach is a high risk of obtaining a model-averaged
posterior estimate that is heavily weighted toward incorrect models that
exclude true values of model parameters.

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigator's choice of priors after having seen the resulting posterior.
%In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
    Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting high prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before
performing the analysis.

@@

\citet{Hickerson2013} present information only on the extreme case of a
single divergence event.
As discussed in \citet{Oaks2012}, it seems odd to consider the estimation
of two divergence events as a success when divergence is random over hundreds
of thousands (or millions) of generations.
In an empirical system such as the Philippines, where island fragmentation has
occurred at least 10 times over the past several millions of years
\citep{Haq1987,Rohling1998,Siddall2003,Miller2005}, an estimate where 22 taxa
share even a handful of divergence events would be of biogeographic interest.

Lastly, \citet{Hickerson2013} translate their results from units of
\globalcoalunit generations to generations assuming a mutation rate of
$1.92\e{-8}$ mutations per site per generation.
If we translate their results to a scale more consistent with rates of mutation
of nuclear loci ($1\e{-9}$), even under the very optimistic prior settings used
by \citet{Hickerson2013} the method can only reliably reject the extreme case
of one divergence event when divergences are random over a period of more than
3 million generations.
Again, considering \citet{Hickerson2013} are assuming prior knowledge that
all population pairs diverged within the last coalescent unit, the
method has low power to detect random variation in divergence times.

@@

Our results presented above that demonstrate the bias of the model-averaging
approach of \citet{Hickerson2013} both toward models with narrower \divt{}
priors (Table~\ref{tabModelChoiceEmpirical} and
Figs.~\labelcref{figExclusionSimTau,figExclusionSimProb,figPowerNumExcluded,figPowerProbExclusion})
and models with fewer \divt{} parameters (Figs.~\ref{figPowerPsiMode} \&
\ref{figPowerOmegaProb}) strongly suggest the primary cause is the uniform
priors reducing the marginal likelihoods of large models.
In all of our model-averaging analyses, all prior models have the same number
of samples.
% Thus, it is difficult to explain the method's propensity toward the model with
% the smallest parameter space via insufficient prior sampling.
While analyses that sample each model proportional to their relative parameter
space could be explored, it seems much more likely that the broad uniform
priors are simply inhibiting the marginal likelihoods of spacious models.

@@

In theory, the approach of \citet{Hickerson2013} is very appealing.  It sums
over multiple candidate prior models to produce a posterior estimate
marginalized over the uncertainty in prior choice.
In general, Bayesian model-averaging is a powerful approach that leverages a
great strength of Bayesian statistical procedures, namely the ability to
obtain marginalized estimates that incorporate uncertainty in nuisance
parameters.
However, given the basic \msb model is already struggling to estimate
a huge number of parameters and model probabilities with scant information
from the data, it is not surprising that adding another dimension of
model choice to the method causes problems.

@@

% Importantly, this strategy is easy to implement.
Given that ABC methods only need to draw random values from prior distributions
(hence there are no difficult prior and proposal ratios to calculate, etc.) it
is easy to use the most appropriate distributions on parameters.
Also, this approach reduces the temptation of empirically guided priors.
The investigator can place the majority of the prior density in regions of
parameter space they believe, \emph{a priori}, are most plausible, but still
capture uncertainty in the tails of distributions with low density.
As discussed in \citet{Oaks2012} the use of uniform priors necessitate
broad priors to avoid excluding the truth \emph{a priori}.
Thus, to avoid the behavior of the method under these uniform priors, using the
data is a very tempting, albeit risky, option \citep{Hickerson2013}.
More appropriate prior distributions would alleviate this issue.

### 2013-10-18 manuscripts/reply/reply.tex
Incorporating comments from Mark.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, criticising the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, questioning the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.
